Interpretable Machine Learning

### 2019-07-04 chunks/story-wines.Rmd
finalizes talk\

##  {.emphasizedabit}
Predict wine quality from its physicochemical properties.

## {.center data-background=../images/minho.png data-background-size=contain}

@@

## {.center data-background=../images/wine-features.jpg data-background-size=contain}

## Quality Distribution

@@

# How can we solve this problem?

## 
```{r}
knitr::include_graphics("../images/checkmark.png")
```

>>>>

# Let's Predict Wine Quality

## 
```{r, out.width = "100%"}
knitr::include_graphics("../images/wine-features.jpg")
```

# How can we develop a wine quality prediction program?

@@

## Wine Quality Distribution

@@
